Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-10 ms.tex
Fixing some table labels

  {$\left(\frac{t_{\rm cool}}{t_{\rm
          ff}}\frac{0.2}{\eta}\right)_{r_s}^{(d)}$} & Issues? \\

@@

\label{table:models}  
\end{tabular}
\begin{tablenotes}
\item $^{(a)}$ Inner power-law index of stellar Nuker profile.
  $^{(b)}$ Break radius of stellar Nuker profile.  $^{(c)}$Accretion
  rate in Eddington units, normalized to a stellar mass input
  parameter $\eta = 0.2$.  $^{(d)}$Ratio of cooling timescale to
  free-fall timescale at stagnation radius.  Thermally unstable
  solutions are shown in bold text.  $\dagger$Calculated with
  radiative cooling included, assuming mass loss parameter $\eta =
  0.2$.  $\ddagger$Calculated with radiative cooling and conductivity
  included, assuming mass loss parameter $\eta = 0.2$ and conductivity
  saturatioon parameter $\phi=0.1$ (recall that we assume that the
  conductive heat flux saturates to $F_{\rm cond}=5\phi \rho c_s^3$). 
\end{tablenotes}
\end{minipage}
\end{threeparttable}

>>>>

  {$\left(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|\frac{0.2}{\eta}\right)_{r_s}^{(d)}$} & Issues? \\

@@

\label{table:models}  
\end{tabular}
\begin{tablenotes}
\item $^{(a)}$ Inner power-law index of stellar Nuker profile.
  $^{(b)}$ Break radius of stellar Nuker profile.  $^{(c)}$Accretion
  rate in Eddington units, normalized to a stellar mass input
  parameter $\eta = 0.2$.  $^{(d)}$Ratio of wind heating rate to
  radiative cooling rate at the stagnation radius.  Thermally unstable
  solutions are shown in bold text.  $\dagger$Calculated with
  radiative cooling included, assuming mass loss parameter $\eta =
  0.2$.  $\ddagger$Calculated with radiative cooling and conductivity
  included, assuming mass loss parameter $\eta = 0.2$ and conductivity
  saturatioon parameter $\phi=0.1$ (recall that the
  conductive heat flux saturates to $F_{\rm cond}=5\phi \rho c_s^3$). 
\end{tablenotes}
\end{minipage}
\end{threeparttable}
